Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
quarto reformatting
Reducing height of figure
Otherwise in visual mode it takes up the entire screen!

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
width="`{julia} ecs_width`" height=500 align="center"}

>>>>

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
width="`{julia} ecs_width`" height="500" align="center"}
